Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-09-25 Paper.Rmd
brain fry

@@

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating. This means that people care more about negative cues than positive cues probably because they want to cut down potential certain losses. A similar result was reflected by the negative coefficient of the proportion of positive words in a review. This shows that reviews with positive sentiments doesn't have a strong diagnostic value for consumers. Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014]. An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021]. The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this. A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded. Since a preference towards a brand is subjective it might be speculated that a strong brand could embed experience attributes into search goods. A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good. That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable is the product image that was created by Apple.

@@

A similar strong support for Negativity Bias can't be observed in the case of movies. Only evidence for Negativity Bias was the significant linear interaction term between Review Length and Review Rating. According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough. This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients there. However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens. This means that potential buyers require more elaboration when a review is rated low. For experience goods, high rated reviews become more helpful on the average when reviews are short. This also might be a sign for positivity bias where people pay more attention to reviews which were aligned with their own feelings [@zhu2021]. Since experience attributes are naturally subjective it is logical to think that readers look for reviews that they agree.

Various reasons could be speculated about why the Hypothesis 5 and Hypothesis 6 didn't hold for experience goods.

-   subjectivity, emolex, heterogeneous opinions, row 10, show other works which are in line with your results,

One reason why the statistical results for search goods came out just as expected can be accredited to their objective features. Properties of electronics are easily evaluated prior purchase. This means that it is comparatively easier to collect information on search goods than experience goods. Other than online consumer reviews on an online retail website, a potential buyer has an arsenal of product reviews which are available on tech enthusiastic websites where electronics are reviewed by professionals. Furthermore, some channels on YouTube offer product reviews where the reviewer inspects the product in question on camera. Thus, the potential buyer can gather a great amount of information even before accessing to the online retailer's website.

>>>>

-   show other works which are in line with your results,

@@

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating. This means that people care more about negative cues than positive cues probably because they want to cut down potential sure losses. A similar result was reflected by the negative coefficient of the proportion of positive words in a review. This shows that reviews with positive sentiments doesn't have a strong diagnostic value for consumers. Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014]. An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021]. The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this. A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded. Since a preference towards a brand is subjective it might be speculated that a strong brand could embed experience attributes into search goods. A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good. That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable most of the time is the product image that was created by Apple.

The rationality why the statistical results for search goods came out just as expected can be accredited to their objective features. Properties of electronics are easily evaluated prior purchase. This means that it is comparatively easier to collect information on search goods than experience goods. Other than online consumer reviews on an online retail website, a potential buyer has an arsenal of product reviews which are available on tech enthusiastic websites where electronics are reviewed by professionals. Furthermore, some channels on YouTube offer product reviews where the reviewer inspects the product in question on a camera. Thus, the potential buyer can gather a great amount of information even before accessing to the online retailer's website.

@@

A similar strong support for Negativity Bias can't be observed in the case of movies. Only evidence for Negativity Bias was the significant linear interaction term between Review Length and Review Rating. According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough. This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients there so no matter the Review Length is U-Shaped function is observed. However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens. This means that potential buyers require more elaboration when a review is rated low. For experience goods, high rated reviews become more helpful on the average when reviews are short. This also might be a sign for positivity bias where people pay more attention to reviews which were aligned with their own feelings [@zhu2021]. Since experience attributes are naturally subjective it is logical to think that readers look for reviews that they agree.

A number of reasons could be speculated about why the Hypothesis 5 and Hypothesis 6 didn't hold for experience goods. The expectation was observing a negative significant coefficient for proportion of positive words and a positive significant coefficient for proportion of negative words. At the very least it can be said that the existence of positive words in a movie review doesn't offer a diagnostic value according to regression results. Thus, it is hard to say there is a strong deviation from Hypothesis 6. On the contrast, Hypothesis 5 for experience goods wasn't supported at all.

One reason of this might be that the NRC Word-Emotion Association Lexicon which was used to mine the negative words in the reviews wasn't suitable for movie reviews. For instance, the word "*cage"* is a negative word in the lexicon and "*marvel*" is a positive word. One or more movies in the sample include movies where "Nicholas *Cage*" had the starring role. There are also "*Marvel* Cinematic Universe" movies present in the data. Cases like these may create noise for the variable and the model because aforementioned words were used frequently and outside of the context of the lexicon. To test this problem words such as "*cage, john, climax, force, king, mad, fury, hardy, margin, harry, marvel, stark, iron, vulture, green, goblin, bale*" were filtered out of the lexicon for both good types. Neither coefficient signs nor coefficient significances were changed. However, it should be pointed out that the coefficient of negative words for experience goods was weakened slightly. Further filtering wasn't pursued because of potential dangers of hypothesis fishing. (The results in Table \@ref(tab:Reg-Results) are the results with the filter.)

-   talk about the correlation table where rating and sentiment has the expected correlations

Another reason may arise from the subjective nature of the experience attributes of the movies. Negative words, in the case of electronics, may have narrower range of meanings because what they try to convey directly relates the to quality of the good itself. The quality of the good is easily accessible because of the fact that electronics have dominant search attributes. Thus, negative words probably translates as potential monetary risks rather than affecting emotions. A risk might be exemplified as purchasing a sub-par performing laptop with a given budget, in other words getting sub-optimal utility. Furthermore, electronics are usually bought to be used for a comparatively long period of time. A smartphone or a television can serve its owner for years so negative cues which relate to below average durability are very important. Buying a sub-durable product for a given budget can only increase the chances that the consumer will have to buy the same type of product prematurely in the future. On the other hand, the monetary risks associated with a bad movie are relatively lower. Consumers can go to cinema, buy a DVD or access the movie as a part of their subscription plan on platforms such as Netflix. Subscription or ticket fees aren't the only cost for the consumer. In order to consume the product the consumer must spend the time that is equal to the duration of the movie. Of course, the consumer can stop watching the movie anytime if it is too unbearable for her so she doesn't waste any more time. Additionally, laptops, phones and televisions could be considered as tools to consume products such as software and media whereas movies themselves can be considered as consumed after they were watched for the first time. Because of these reasons the money spent on a movie might be irrelevant to an average consumer since accessing a movie is relatively cheaper than owning an electronic device. Therefore, negative words in a movie review may not alert the consumer for potential monetary losses. Instead, negative words could render a review in question unpleasant because emotions are priority in the case of consumption of movies.

-   subjectivity, emolex, heterogeneous opinions, row 10,
